Delta Smelt Enclosure Study 2019 Hybrid Paper Diet Analysis

### 2022-11-19 smelt_2019_allseasons/Diet 2019.Rmd
updating diet plots

diet2[diet2$Prey.Taxa %in% c("Americorophium sp.", "Americorophium spinicorne", "Eogammarus confervicolus", "Gammaridea", "Hyallela azteca", "Crangonyx sp.", "Corophiidae", "Amphipoda"),]$Taxa <- "Amphipoda"

diet2[diet2$Prey.Taxa %in% c("Pseudodiaptomus forbesi", "Calanoida", "Eurytemora affinis", "Diaptomidae", "Sinocalanus doerrii", "Osphranticum labronectum"),]$Taxa <- "Calanoida"

diet2[diet2$Prey.Taxa %in% c("Acanthocyclops sp.", "Macrocyclops sp.", "Diacyclops thomasi", "Eucyclops sp.", "Cyclopoida", "Halicyclops sp.", "Mesocyclops sp.", "Tropocyclops sp.", "Tropocyclops sp."),]$Taxa <- "Cyclopoida"

@@

diet2[diet2$Prey.Taxa %in% c("Harpacticoida"),]$Taxa <- "Harpacticoida"

diet2[diet2$Prey.Taxa %in% c("Ostracoda"),]$Taxa <- "Ostracoda"

@@

Cage_type$Cage.ID <- c("A", "B", "C", "D", "E", "F")
Cage_type$Mesh <- c("wrap", "large", "small", "small", "wrap", "large")

@@

#change location titles 
diet$Location[diet$Location =="RIVERS"] <- "RV.Feb"
diet$Location[diet$Location =="Sac DWSC"] <- "DWSC.Apr"
diet$Location[diet$Location =="SM"] <- "SM.Nov"
diet$Location[diet$Location =="YB"] <- "YB.Nov"
#RV a little trickier with two dates
diet$ld = paste(diet$Location, diet$Date)
diet$Location[diet$ld =="RV 2019-08-28"] <- "RV.Aug"
diet$Location[diet$ld =="RV 2019-11-06"] <- "RV.Nov"
RV <- filter(diet, Location == "RV")
diet$Location[diet$ld =="RV 2019-11-07"] <- "RV.Nov"

@@

# prep merged data for taxa proportion
```{r}
unique(diet$Location)

#remove FCCL controls
diet<-diet[diet$Cage.ID != "FCCL Control Tank 1",]
diet<-diet[diet$Cage.ID != "FCCL Control Tank 2",]
diet<-diet[diet$Cage.ID != "FCCL Control",]

#remove DWSC
#diet<-diet[diet$Location != "DWSC.Apr",]

@@

str(diet)
#change count to numeric
diet$Count<-as.numeric(diet$Count)
#output says NAs introduced by coercion - check NA's
newDF <- diet[is.na(diet$Count),]
#one NA next to a gammaridae - comment says that it was too digested and could be more than one individual, to be safe just going to add a count of "1" for this observation; found it on row 413
diet<-diet %>% replace_na(list(Count=1))
#change count to numeric
diet$Count<-as.numeric(diet$Count)

@@

#select columns I want for proportion
full.prop.3<-subset(full.prop.2, select=c("Location", "Mesh", "tlc", "Taxa", "proportion"))
#replace proportion Nas with zeros
diet.prop<-full.prop.3 %>% replace_na(list(proportion=0))

@@

# plot number of empty stomachs
## these will not be included in the 100% stacked bar later
```{r}
#order locations
stomach_abundance$Location <- stomach_abundance$Location.x
stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("DWSC.Apr", "RV.Feb", "RV.Aug", "SM.Nov", "YB.Nov", "RV.Nov"))

@@

#order locations
prop$Location <- ordered(prop$Location, levels = c("DWSC.Apr", "RV.Feb", "RV.Aug", "RV.Nov", "YB.Nov", "SM.Nov"))

cbPalette <- c("#F0E442", "#E69F00", "#009E73", "#56B4E9", "#CC79A7", "#D55E00", "#0072B2")
legend_title <- "Taxa"

ggplot(data=prop, aes(x=Location, y =prop.mean)) +
    geom_bar(aes(fill=factor(Taxa, levels=c("Amphipoda", "Calanoida", "Cladocera", "Cyclopoida", "Diptera", "Harpacticoda", "Ostracoda", "Other"))),  position="fill", stat="identity") +
  theme_bw() + 
  scale_fill_manual(legend_title, values=cbPalette)+
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Mean Contribution to Diet")
```

>>>>

diet2[diet2$Prey.Taxa %in% c("Americorophium sp.", "Americorophium spinicorne", "Eogammarus confervicolus", "Gammaridea", "Hyallela azteca", "Crangonyx sp.", "Corophiidae", "Amphipoda"),]$Taxa <- "Amphipod"

diet2[diet2$Prey.Taxa %in% c("Pseudodiaptomus forbesi", "Calanoida", "Eurytemora affinis", "Diaptomidae", "Sinocalanus doerrii", "Osphranticum labronectum"),]$Taxa <- "Calanoid"

diet2[diet2$Prey.Taxa %in% c("Acanthocyclops sp.", "Macrocyclops sp.", "Diacyclops thomasi", "Eucyclops sp.", "Cyclopoida", "Halicyclops sp.", "Mesocyclops sp.", "Tropocyclops sp.", "Tropocyclops sp."),]$Taxa <- "Cyclopoid"

@@

diet2[diet2$Prey.Taxa %in% c("Harpacticoida"),]$Taxa <- "Harpacticoid"

diet2[diet2$Prey.Taxa %in% c("Ostracoda"),]$Taxa <- "Ostracod"

@@

Cage_type$Cage.ID <- c("A", "B", "C", "D", "E", "F")
Cage_type$Mesh <- c("small", "large", "wrap", "wrap", "small", "large")

@@

#change location titles 
diet$Location[diet$Location =="RIVERS"] <- "RV.Winter"
diet$Location[diet$Location =="Sac DWSC"] <- "DWSC.Winter"
diet$Location[diet$Location =="SM"] <- "SM.Fall"
diet$Location[diet$Location =="YB"] <- "YB.Fall"
#RV a little trickier with two dates
diet$ld = paste(diet$Location, diet$Date)
diet$Location[diet$ld =="RV 2019-08-28"] <- "RV.Summer"
diet$Location[diet$ld =="RV 2019-11-06"] <- "RV.Fall"
RV <- filter(diet, Location == "RV")
diet$Location[diet$ld =="RV 2019-11-07"] <- "RV.Fall"

@@

# prep merged data for taxa proportion
```{r}
#remove FCCL controls
diet<-diet[diet$Cage.ID != "FCCL Control Tank 1",]
diet<-diet[diet$Cage.ID != "FCCL Control Tank 2",]
diet<-diet[diet$Cage.ID != "FCCL Control",]

@@

#change count to numeric
diet$Count<-as.numeric(diet$Count)

#output says NAs introduced by coercion - check NA's
newDF <- diet[is.na(diet$Count),]

#one NA next to a gammaridae - comment says that it was too digested and could be more than one individual, to be safe just going to add a count of "1" for this observation; found it on row 413
diet<-diet %>% replace_na(list(Count=1))

#change count to numeric
diet$Count<-as.numeric(diet$Count)

@@

#select columns I want for proportion
full.prop.3<-subset(full.prop.2, select=c("Location", "Mesh", "tlc", "Taxa", "proportion"))

#replace proportion Nas with zeros
diet.prop<-full.prop.3 %>% replace_na(list(proportion=0))

@@

# plot number of empty stomachs
## these will not be included in the 100% stacked bar later
```{r}
#order locations
stomach_abundance$Location <- stomach_abundance$Location.x
stomach_abundance$Location <- ordered(stomach_abundance$Location, levels = c("DWSC.Winter", "RV.Winter", "RV.Summer", "SM.Fall", "YB.Fall", "RV.Fall"))

@@

#order locations
prop$Location <- ordered(prop$Location, levels = c("DWSC.Winter", "RV.Winter", "RV.Summer", "RV.Fall", "YB.Fall", "SM.Fall"))

#order taxa to match zoop plot
prop$Taxa <- factor(prop$Taxa, levels=c("Calanoid", "Cladocera", "Cyclopoid", "Harpacticoid", "Ostracod", "Other", "Amphipod", "Diptera"))

ggplot(data=prop, aes(x=Location, y =prop.mean, fill=Taxa)) +
    geom_bar(position="fill", stat="identity", colour="black") +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Mean Contribution to Diet")

ggsave("smelt_2019_allseasons/figures/diet19_onepanel.png", dpi=250, height=4.5, width=7, units="in")

#facet by season

#create season column
prop2 <- prop
prop2$Season <- "NA"
prop2[prop2$Location %in% c("DWSC.Winter", "RV.Winter"),]$Season <- "Winter"
prop2[prop2$Location %in% c("RV.Summer"),]$Season <- "Summer"
prop2[prop2$Location %in% c("RV.Fall", "YB.Fall", "SM.Fall"),]$Season <- "Fall"

#change Location to drop season
prop2$Location <- as.character(prop2$Location)
prop2$Location[prop$Location =="DWSC.Winter"] <- "DWSC"
prop2[prop2$Location %in% c("RV.Winter", "RV.Summer", "RV.Fall"),]$Location <- "RV"
prop2$Location[prop$Location =="YB.Fall"] <- "YB"
prop2$Location[prop$Location =="SM.Fall"] <- "SM"

#order seasons
prop2$Season <- factor(prop2$Season, levels=c("Winter", "Summer", "Fall"))

#order locations
prop2$Location <- factor(prop2$Location, levels=c("DWSC", "RV", "YB", "SM"))

#order taxa to match zoop plot
prop2$Taxa <- factor(prop2$Taxa, levels=c("Calanoid", "Cladocera", "Cyclopoid", "Harpacticoid", "Ostracod", "Other", "Amphipod", "Diptera"))

#plot
ggplot(data=prop2, aes(x=Location, y =prop.mean, fill=Taxa)) +
  geom_bar(position="fill", stat="identity", colour="black", width=0.75) +
  facet_wrap(~Season, ncol=1) +
  theme_bw() +
  viridis::scale_fill_viridis(discrete = TRUE, option = "plasma") +
  theme(legend.position="right", axis.title.x = element_blank())+
  labs(y = "Mean Contribution to Diet") +
   theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10))

library(scales)
show_col(viridis_pal(option = "plasma")(8))
viridis_pal(option = "plasma")(8)

ggsave("smelt_2019_allseasons/figures/diet19_multipanel.png", dpi=250, height=6, width=6, units="in")
```
